---
title: "hana Web & SEO Dashboard "
resource_files:
- inc/web_seo_data.RData
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme: readable
    orientation: columns
    logo: inc/hana_logo_small.png
    css: inc/corp-styles.css
    includes:
      before_body: "inc/google-analytics.js"
---

```{r setup, include=FALSE}
library(shiny)
library(flexdashboard)
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(ggplot2)
library(plotly)
library(scales)
library(here)
library(rlang)
library(RiHana)

 month_to_date<-lubridate::floor_date(Sys.Date(), unit="month")


load('inc/web_seo_data.RData')
 


updatedWebData <- reactive({
  web_data <-web_data_all_edited %>% 
    filter(grepl(paste0(input$WebChannel,collapse = "|"),channel),
           grepl(input$WebEntryPage,landing_content),
           dau_date>=input$WebTimeRange[1],
           dau_date<=input$WebTimeRange[2]) %>% 
    mutate(timespan=case_when(
           input$WebTimeDimension=='Week'~week_start,
           input$WebTimeDimension=='Month'~month_start,
           input$WebTimeDimension=='Quarter'~quarter_start)) %>% 
    group_by(timespan,channel) %>% 
    summarise(Active_Users=sum(active_users),
              `Lead Form Views`=sum(lead_forms_viewed),
              `Lead Form Submissions`=sum(lead_forms_submitted),
              `Form Conversion`=sum(lead_forms_submitted)/sum(lead_forms_viewed),
              `Site Conversion`=sum(lead_forms_submitted)/sum(Active_Users)) %>% 
  rename_at(vars(starts_with(input$WebMeasure)), list(~paste0("measure"))) %>% 
  select(timespan,channel,measure)

    # summarise(measure=case_when(
    #   input$WebMeasure == 'Sessions'~sum(visits),
    #   input$WebMeasure == 'Lead Form Views'~sum(lead_forms_viewed),
    #   input$WebMeasure == 'Lead Form Submissions'~sum(lead_forms_submitted),
    #   input$WebMeasure == 'Form Conversion'~sum(lead_forms_submitted)/sum(lead_forms_viewed),
    #   input$WebMeasure == 'Site Conversion'~sum(lead_forms_submitted)/sum(visits))
    #)

  return(web_data)
})


updatedContentData <- reactive({
 content_data<-web_content_all_edited %>% 
#   mutate(full_url=paste0(host,"/",page)) %>% 
  filter(grepl(input$WebFilter,url,ignore.case=TRUE),
#         !grepl('hana-qa',page),
         grepl(paste0(input$WebChannel,collapse = "|"),channel),
         grepl(input$WebEntryPage,landing_content),
        seg_date>=input$WebTimeRange[1],
         seg_date<=input$WebTimeRange[2]) %>% 
   left_join(web_converters) %>% 
  group_by(path) %>% 
  summarise(users=n_distinct(anonymous_id),
            converters=n_distinct(converted_id,na.rm=TRUE)) %>% 
  arrange(desc(users)) %>% 
  slice(1:10) %>% 
  arrange(users) %>% 
  mutate(page=forcats::as_factor(path))
  
  return(content_data)
})



updatedWebConversion <- reactive({
  
  web_data <-web_data_all_edited %>% 
    filter(grepl(paste0(input$WebChannel,collapse = "|"),channel),
           grepl(input$WebEntryPage,landing_content),
           dau_date>=input$WebTimeRange[1],
           dau_date<=input$WebTimeRange[2]) %>% 
    summarise(active_users=sum(active_users),
              lead_form_views=sum(lead_forms_viewed),
              lead_form_submissions=sum(lead_forms_submitted),
              form_conversion=round((lead_form_submissions/lead_form_views)*100,1),
              site_conversion=round((lead_form_submissions/active_users)*100,1))

  
  return(web_data)
})

updatedLeadData <- reactive({
  lead_data <-digital_leads %>% 
    filter(grepl(paste0(input$WebChannel,collapse="|"),digital_channel),
           grepl(input$WebEntryPage,landing_content),
           create_date>=input$WebTimeRange[1],
           create_date<=input$WebTimeRange[2]) %>% 
    mutate(timespan=case_when(
           input$WebTimeDimension=='Week'~create_week,
           input$WebTimeDimension=='Month'~create_month,
           input$WebTimeDimension=='Quarter'~create_quarter)) %>% 
    group_by(tracking_code) %>% 
    summarise(leads=n()) %>% 
    arrange(leads) %>% 
    mutate(tracking_code=forcats::as_factor(tracking_code))
    
  return(lead_data)
})

searchConsoleSummaryData <- reactive({
  keyword_data<-search_console_keyword_performance_edited %>% 
    filter(grepl(input$SEOKeyword,keyword,ignore.case=TRUE),
           grepl(paste0(input$KeywordCategory,collapse="|"),branded,ignore.case=TRUE),
           grepl(paste0(input$KeywordSearchType,collapse="|"),search_type,ignore.case=TRUE),
           grepl(paste0(input$KeywordDevice,collapse="|"),device,ignore.case=TRUE),                                                  
           grepl(paste0(input$KeywordCountry,collapse="|"),country,ignore.case=TRUE)) %>% 
    mutate(timespan=case_when(
      input$WebTimeDimension=='Week'~search_week,
      input$WebTimeDimension=='Month'~search_month,
      input$WebTimeDimension=='Quarter'~search_quarter)) %>% 
    group_by(timespan) %>% 
    summarise(Impressions=sum(impressions),
                            Clicks=sum(clicks),
                            AvgRank=sum(agg_rank)/sum(impressions)) %>% 
    rename_at(vars(starts_with(input$SEOMeasure)), list(~paste0("measure"))) 
})


searchConsoleKeywordData <- reactive({
  keyword_data<-search_console_keyword_performance_edited %>% 
                  filter(grepl(input$SEOKeyword,keyword,ignore.case=TRUE),
                         grepl(paste0(input$KeywordCategory,collapse="|"),branded),
                         grepl(paste0(input$KeywordSearchType,collapse="|"),search_type,ignore.case=TRUE),
                         grepl(paste0(input$KeywordDevice,collapse="|"),device,ignore.case=TRUE),                                                  
                         grepl(paste0(input$KeywordCountry,collapse="|"),country,ignore.case=TRUE)) %>% 
                      mutate(timespan=case_when(
                        input$WebTimeDimension=='Week'~search_week,
                        input$WebTimeDimension=='Month'~search_month,
                        input$WebTimeDimension=='Quarter'~search_quarter)) %>% 
    group_by(keyword,timespan) %>% 
                  summarise(avg_rank=sum(agg_rank)/sum(impressions)) %>% 
                  inner_join(search_console_keyword_performance_edited %>% 
                               filter(grepl(input$SEOKeyword,keyword,ignore.case=TRUE),
                                      grepl(paste0(input$KeywordCategory,collapse="|"),branded),
                                      grepl(paste0(input$KeywordSearchType,collapse="|"),search_type,ignore.case=TRUE),
                                      grepl(paste0(input$KeywordDevice,collapse="|"),device,ignore.case=TRUE),                                                  
                                      grepl(paste0(input$KeywordCountry,collapse="|"),country,ignore.case=TRUE)) %>% 
                               group_by(keyword) %>% 
                               summarise(impressions=sum(impressions)) %>% 
                               arrange(desc(impressions)) %>% 
                               slice(1:10) %>% 
                               select(keyword))
  
  
})
```


Sidebar {.sidebar }
=====================================
###### **Data Updated:** _`r file.info('inc/web_seo_data.RData')$mtime` ._

```{r}


dateRangeInput('WebTimeRange',
      label = 'Choose the time range',
      min=RiHana::get_relevant_date()$yoy_date,
      max=RiHana::get_relevant_date()$yesterdays_date,
      start = RiHana::get_relevant_date()$ytd_date, 
      end = RiHana::get_relevant_date()$yesterdays_date,
      weekstart = 1
    )


radioButtons("WebTimeDimension",label="Pick the time interval",
             choices=c("Week","Month","Quarter"),
             selected="Month")
helpText("Note: Time interval specifies the X axis where appicable for trending data")


selectizeInput(
        'WebChannel', 'Choose a channel', choices = unique(web_data_all_edited$channel),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)


selectInput("WebEntryPage", label = "Choose an Entry Page Category",
            choices = c("All" ="*",
                        "Landing" = "Landing Page",
                        "Blog" = "Blog",
                        "WWW" = "WWW"), 
            selected = c("All"),
            multiple = FALSE)


```

<strong>Channel</strong> - How did the visitor arrive to the website

<strong>Active Users</strong> - Count of uniquely identified daily users in a given time frame

<strong>Lead Form Views</strong> - Number of website visits that contained at least one view of a lead form

<strong>Lead Form Submissions</strong> - Number of website visits that contained at least one lead form submission

<strong>Form Conversion</strong> - Lead Form Submissions / Lead Form Views

<strong>Site Conversion</strong> - Lead Form Submissions / Active Users

<strong>Site Conversion</strong> - Lead Form Submissions / Active Users

```{r }

helpText("Note: Text fields (Filter Content and Keyword) support Regular Expression Searches.  You can use '|' as an 'or' (e.g., Dallas|Irvine).  You can also use '.*' as a wildcard (e.g. Dallas.*Free) for fuzzy searches.")

```

Website Performance 
===================================== 

Column{data-height=650,width=8}
-------------------------------------

### Web Performance

```{r }
fillRow(
fillCol(flex=c(2,1,9),
        fillRow(
          renderGauge({
            web_conversion_dat<-updatedWebConversion()
            gauge(web_conversion_dat$form_conversion,
                  label="Form Conversion", 
                  min = 0, max = 50, 
                  symbol = '%', 
                  gaugeSectors(
                    success = c(30, 50), 
                    warning = c(10, 29), 
                    danger = c(0, 9)
                    ))
            }),
          renderGauge({
            site_conversion_dat<-updatedWebConversion()
            gauge(site_conversion_dat$site_conversion,
                  label="Site Conversion", 
                  min = 0, max = 10, 
                  symbol = '%', 
                  gaugeSectors(
                    success = c(5, 10), 
                    warning = c(2, 4), 
                    danger = c(0, 1)
                    ))
            })
          ),
        selectInput("WebMeasure", label = "Choose a metric",
            choices = c("Active_Users","Lead Form Views","Lead Form Submissions","Form Conversion","Site Conversion"), 
            selected = c("Active_Users"),
            multiple = FALSE),
        renderPlotly({
          web_dat<-updatedWebData()
          bar_type<-ifelse(input$WebMeasure %in% c("Form Conversion","Site Conversion"),"group","stack")
          plot_ly(web_dat,
#                  marker = list(color = "#002D36"),
                  y = ~measure,
                  x= ~timespan,
                  color=~channel,
                  colors = hana_color_palette(n_distinct(web_dat$channel)),
                  type="bar") %>% 
            layout(
#              barmode = "group",
              barmode=bar_type,
              bargap=0.1,
              legend = list(orientation = 'h'),
              title = input$WebMeasure,
              yaxis = list(title=input$WebMeasure))
          })
    ),
fillCol(flex=c(5,1,6),
        fillRow(
renderPlotly({
  m <- list(
  l = 250,
  r = 25,
  b = 25,
  t = 25,
  pad = 4
)
  content_dat<-updatedContentData()
  plot_ly(content_dat,
        marker = list(color = "#002D36"),
        orientation='h',
        y = ~page,
        x= ~users,
        name='Users',
        type="bar")%>%
    add_trace(x=~converters,name='Converters',marker = list(color = "#977124")) %>% 
  layout(barmode = 'group',
         title = 'Top Content',
         legend = list(orientation = 'h'),
         margin=m)

})
)
,
fillRow(textInput("WebFilter", 
          label = "Filter Content:",
          placeholder="*",
          width="25%")
),

fillRow(
renderPlotly({
  lead_dat<-updatedLeadData()
  plot_ly(lead_dat,
        marker = list(color = "#002D36"),
        orientation='h',
        y = ~tracking_code,
        x= ~leads,
        name='Leads',
         type="bar") %>% 
      layout(title = 'Top Lead Types')


})   
)
)
)
```

SEO
===================================== 

Column
-------------------------------------

### SEO
```{r }
fillCol(flex=c(1,2),
        fillRow(flex=c(6,5,5),
        renderPlotly({
          referring_domains_dat<-ahrefs_referring_domains_edited
          plot_ly(referring_domains_dat,
                  marker = list(color = "#002D36"),
                  y = ~referring_domains,
                  x= ~date,
                  type="bar") %>% 
      layout(title = 'Referring Domains')
          }),
        renderPlotly({
          domain_rank_dat<-ahrefs_domain_rank_edited
          plot_ly(domain_rank_dat,
                  marker = list(color = "#002D36"),
                  y = ~domain_rank,
                  x= ~week,
                  type="bar") %>% 
      layout(title = 'Domain Rank')
          }),
        renderPlotly({
          backlinks_dat<-ahrefs_backlinks_edited
          plot_ly(backlinks_dat,
                  marker = list(color = "#002D36"),
                  y = ~backlinks,
                  x= ~date,
                  type="bar") %>% 
      layout(title = 'Backlinks')
          })
        ),
      fillRow(flex=c(1,3,4),
        wellPanel(
        textInput("SEOKeyword", 
          label = "Keywords:",
          placeholder="*"),
        selectizeInput(
        'KeywordCategory', 'Keywords to include', choices = unique(search_console_keyword_performance_edited$branded),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
          ),
        selectizeInput(
        'KeywordCountry', 'Countries to include', choices = unique(search_console_keyword_performance_edited$country),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
        ),
        selectizeInput(
        'KeywordSearchType', 'Search type to include', choices = unique(search_console_keyword_performance_edited$search_type),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
        ),
        selectizeInput(
        'KeywordDevice', 'Search device to include', choices = unique(search_console_keyword_performance_edited$device),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
        )
        ),
      fillCol(flex=c(3,1),
              renderPlotly({
                  keyword_summary_dat<-searchConsoleSummaryData()

                keyword_summary_dat %>%
                  plot_ly(line = list(color = "#002D36"),
                          y = ~measure,
                          x= ~timespan,
                          type = 'scatter', 
                          mode = 'lines') %>% 
      layout(title = 'SEO Trend',
             yaxis = list(title=input$SEOMeasure))
              }),
      selectInput("SEOMeasure", label = "Choose a metric",
            choices = c("Impressions","Clicks","AvgRank"), 
            selected = c("AvgRank"),
            multiple = FALSE)      
              ),
              renderPlotly({
                  keyword_performance_dat<-searchConsoleKeywordData()
                keyword_performance_dat %>%
                  plot_ly(marker = list(color = "#002D36"),
                  y = ~avg_rank,
                  x= ~timespan,
                  color=~keyword,
                  type = 'scatter', 
                  mode = 'lines') %>% 
      layout(title = 'Keyword Performance')
              })

      )
      )        
```


